Converting LaTeX Legacy R Journal Articles into R Markdown Articles using texor and rebib

### 2023-08-28 texor.Rmd
may still need to add more problems to the list

The code is designed to process an issue at a time, by operating on all the files in the directory housing the issue. Each processing function, from pre-processing the text in the LaTeX file to post-processing accepts a directory name as the argument.  The vignette [Introduction to texor](https://abhi-1u.github.io/texor/articles/introduction-to-texor.html) provides more details.

@@

>>>>

The code is designed to process all the articles in an issue at a time, by operating on all the files in the directory housing the issue. Each processing function, from pre-processing the text in the LaTeX file to post-processing accepts a directory name as the argument. Generally, if a problem is encountered with one article, the processing will skip on to the next. The vignette [Introduction to texor](https://abhi-1u.github.io/texor/articles/introduction-to-texor.html) provides more details.

@@

The problems encountered with some articles include:

- The table format is often not as neat in the HTML as in the LaTeX. It can be made close to the original with extra effort in the R Markdown description.
- Some of the figure files are missing - so the figure may need to be extracted from the pdf file and included with `knitr::include_graphics()`.

### 2023-08-28 texor.tex
may still need to add more problems to the list

The code is designed to process an issue at a time, by operating on all the files in the directory housing the issue. Each processing function, from pre-processing the text in the LaTeX file to post-processing accepts a directory name as the argument. The vignette \href{https://abhi-1u.github.io/texor/articles/introduction-to-texor.html}{Introduction to texor} provides more details.

@@

>>>>

The code is designed to process all the articles in an issue at a time, by operating on all the files in the directory housing the issue. Each processing function, from pre-processing the text in the LaTeX file to post-processing accepts a directory name as the argument. Generally, if a problem is encountered with one article, the processing will skip on to the next. The vignette \href{https://abhi-1u.github.io/texor/articles/introduction-to-texor.html}{Introduction to texor} provides more details.

@@

The problems encountered with some articles include:

\begin{itemize}
\tightlist
\item
  The table format is often not as neat in the HTML as in the LaTeX. It can be made close to the original with extra effort in the R Markdown description.
\item
  Some of the figure files are missing - so the figure may need to be extracted from the pdf file and included with \texttt{knitr::include\_graphics()}.
\end{itemize}
